A User-Extensible and Adaptable Parser Architecture

### 2008-12-03 doc/sgai-2008-slides.tex
Lots of improvements to the slides.

\documentclass{beamer}
%\mode<presentation>
%{
%  \usetheme{Warsaw}
%  % or ...
%
%  \setbeamercovered{transparent}
%  % or whatever (possibly just delete it)
%}
\useoutertheme{infolines}

@@

@@

%% Delete this, if you do not want the table of contents to pop up at
%% the beginning of each subsection:
%\AtBeginSubsection[]
%{
%  \begin{frame}<beamer>{Outline}
%    \tableofcontents[currentsection,currentsubsection]
%  \end{frame}
%}

% If you wish to uncover everything in a step-wise fashion, uncomment
% the following command:

%\beamerdefaultoverlayspecification{<+->}

@@

\begin{frame}
    \titlepage{}
\end{frame}

% XXX MAYBE REMOVE THIS
\begin{frame}{Outline}
    \tableofcontents{}
    % You might wish to add the option [pausesections]
\end{frame}

@@

@@

        \item [Aim] To improve SMTP-time anti-spam restriction / measures /
            techniques.

@@

@@

    This requires a parser for Postfix log files.

@@

\section{XXX}

\begin{frame}{XXX}

@@

        \item Postfix log lines change over time and from site to site, so
            it must be easy for the end user to parse new lines.

        \item The processing required for a type of line (e.g.\ remote
            server connecting to send mail) rarely changes, but it can be
            quite complex.

        \item By separating parsing of lines from processing of lines, we
            can make parsing new lines as easy as possible, while still
            allowing for complicated processing when necessary.

@@

@@

        \item [Framework] The framework handles loading rules and providing
            services to actions, e.g.\ data storage.  The framework tries
            each rule in turn until one matches, then it invokes the action
            specified by the rule.

@@

\section{Features}

\begin{frame}{Features}

@@

        \item Cascaded parsing.

        \item The parser does not need to be recompiled when rules are
            changed.

        \item Different rulesets can easily be used.

        \item Rules can be added by actions while the parser is running,
            allowing dynamically changing parsing, e.g.\ macros.

@@

@@

        \item Rules are sorted by how frequently they match.

        \item Architecture scales linearly as the number of rules
            increases.

        \item Performance is \ldots{} XXX

@@

\begin{frame}{Results.}

@@

        \item XXX rules.

@@

@@

@@

        \item The \alert{first main message} of your talk in one or two lines.

        \item The \alert{second main message} of your talk in one or two lines.

        \item Perhaps a \alert{third message}, but not more than that.

>>>>

\documentclass{beamer}
%\mode<presentation>
%{
%  \usetheme{Warsaw}
%  % or ...
%
%  \setbeamercovered{transparent}
%  % or whatever (possibly just delete it)
%}
\useoutertheme{infolines}
\defbeamertemplate*{headline}{JT theme}{}

@@

\newcommand{\timingnote}[1]{%
    \textbf{#1}%
}

@@

@@

\begin{frame}
    \timingnote{30 seconds}
    \titlepage{}
\end{frame}

\begin{frame}{Outline of this talk}
    \timingnote{30 seconds --- 1 minute}
    \tableofcontents{}
\end{frame}

@@

    \timingnote{1--2 minutes}

    This parser architecture was developed as part of a larger project to
    improve anti-spam techniques.

@@

        \item [Currently] Most anti-spam techniques are content-based, and
            require each mail to be accepted before determining its spam
            status.

        \item [However] Rejecting mail at SMTP-time is more efficient, and
            senders of non-spam mails that are incorrectly rejected will be
            informed immediately.

        \item [Project Aim] To improve SMTP-time anti-spam techniques, by
            providing a platform for reasoning about anti-spam techniques.

@@

        \item [XXX] This requires a parser for Postfix log files.

@@

@@

\section{Input characteristics}

\begin{frame}{Input characteristics}

    \timingnote{1 minute}

@@

        \item Postfix log lines change over time and from site to site, so
            it must be easy for the end user to parse new log lines.

        \item The processing required for a type of log line (e.g.\ a
            remote server connecting to send mail) rarely changes, but it
            can be quite complex.

        \item By separating parsing of log lines from processing of log
            lines, we can make parsing new or changed log lines as easy as
            possible, while still allowing for complicated processing when
            necessary.

@@

    \timingnote{2 minutes}

    The architecture is divided into three parts:

@@

        \item [Framework] The framework handles loading rules and providing
            services (XXX BETTER WORD\@?) to actions, e.g.\ data storage,
            inter-action communication, XXX ANOTHER EXAMPLE\@.  For each
            input log line, the framework tries each rule in turn until one
            matches, then it invokes the action specified by the rule.

@@

\section{Features of the Architecture}

\begin{frame}{Features of the Architecture}

    \timingnote{2 minutes}

@@

        \item Cascaded Parsing.  XXX SHOULD I HAVE A REFERENCE\@?

        \item The parser does not need to be recompiled when rules are
            changed, allowing: quicker testing of modified rules; different
            rulesets can easily be used; combining two or more rulesets.

        \item Rules can be changed or added by actions while the parser is
            running, allowing dynamically changing parsing, e.g.\ macros.
            This feature must be used with care.

        \item The architecture is capable of parsing inputs that are not
            completely understood, e.g.\ when developing a parser: the
            framework will warn about unparsed inputs but will continue on
            parsing as best it can.

        \item Parsing can optionally be stateful, e.g.\ parsing a
            programming language.

@@

    \timingnote{2 minutes}

@@

        \item Median throughput when parsing 93 log files is 80.85~MB
            (480,569 log lines) parsed per minute.

        \item Rules are tagged with the name of a Postfix daemon, and will
            only be used to parse log lines produced by that daemon.

        \item Rules are sorted by how frequently they match, resulting in a
            mean reduction of 14.78\% in parsing time compared to using
            unsorted rules.

        \item The architecture scales extremely well as the number of rules
            increases: a 46.05\% increase in Postfix ruleset resulted in a
            mean increase of 0.63\% in parsing time.

        \item Parsing time scales linearly with input size, but is affected
            by input content.

@@

\begin{frame}{Results}

    \timingnote{1--2 minutes}

@@

        \item 169 rules: the top 10\% match 85.03\% of log lines, the
            remainder tailing off similar to a Power Law distribution.

@@

\section{Future Directions}

\begin{frame}{Future Directions}

    \timingnote{1--2 minutes}

        \item Use Machine Learning instead of writing rules; Instance Based
            Learning techniques a requirement due to the size of the data
            set.

        \item Detection of overlapping rules.

        \item XXX REFERENCE IMPLEMENTATION\@?

@@

    \timingnote{1 minute}

@@

        \item East to develop a flexible yet strict parser.

        \item Easy for users to parse new or changed inputs.

        \item Parser can still be efficient and fast.

    \timingnote{remainder}

        \item XXX MAYBE ON A SEPARATE SLIDE\@?

        \item Questions?

        \item Comments?

        \item Suggestions?
